### 2022-01-18 src-latex/main-paper.tex
updated section 5

\section*{Acknowledments and Thanks}
This work is supported by the French National Research Agency (ANR), as part of the SODUCO project, under Grant ANR-18-CE38-0013.

>>>>

\section*{Acknowledments}
This work is supported by the French National Research Agency (ANR), as part of the SODUCO project, under Grant ANR-18-CE38-0013.

### 2022-01-18 src-latex/parts/50-xp-setup.tex
updated section 5

\subsubsection{Spacy}
We used the French model \textit{fr\_core\_news\_lg} provided by Spacy\mcite{spacy} library and leveraged the library utilities to fine-tune it with various training and validation datasets derived from our ground truth dataset (see section 5.2 for details). The base model is fine-tuned in turn with each of the 8 generated training data sets, using the same training parameters. Early stopping is activated with patience parameters set at 1600. For each size of training dataset, 5 runs are performed, always with the same parameters, and the mean value of each performance score is computed.

@@

\subsubsection{Huggingface CamemBERT}
We started from the CamemBERT-ner model already fine-tuned on WikiNER-fr corpus and published on the Hugging Face repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}}. Its output layer is a linear model with a Softmax function. Two NER models are derived from this base model.

\textcolor{green}{Ex 2: On garde CamemBERT et CamemBERT pretrained fine-tuned sur le train clean (patience = 5), validé avec dev clean. Teste les deux modèles sur les trois datasets de test.}

The base model is pretrained on 845 000 entries extracted with PERO OCR for the Next  Sentence  Prediction  (NSP) and  Masked  Language  Model(MLM) tasks. Then it is fine-tuned with the same parameters and on the same training datasets as the first model.

>>>>

\subsubsection{Spacy}
We use the French model \textit{fr\_core\_news\_lg} provided by Spacy\mcite{spacy} library and leverage the library utilities to fine-tune it with various training and validation datasets derived from our ground truth dataset (see section 5.2 for details). The base model is fine-tuned in turn with each of the 8 generated training datasets, using the same training parameters. Early stopping is activated with patience parameters set at 1600. For each size of training dataset, 5 runs are performed, always with the same parameters, and the mean value of each performance score is computed.

@@

\subsubsection{Huggingface CamemBERT}
We start from the CamemBERT-ner model already fine-tuned on WikiNER-fr corpus and published on the Hugging Face repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}}. Its output layer is a linear model with a Softmax function. Four NER models are derived from this base model:

\textit{BERTreference} The base model is fine-tuned in turn on each of the training datasets generated from the groundtruth corpus. Training parameters are set depending on the considered experiment: early stopping is activated with patience parameter set at 3 for experiment 1 and at 5 for experiment 2. \nathalie{<-- bertrand tu peux vérifier si c'est OK stp?}

\textit{BERTpero-ocr} This model is used for experiement 2 only. The base model is fine-tuned on the training dataset generated by projecting the named entities annotation on the text extracted by PERO OCR, using the same parameters as for the \textit{BERTreference} model.

\textit{BERTptrn-reference} The base model is pretrained on 845 000 entries extracted with PERO OCR for the Next  Sentence  Prediction  (NSP) and  Masked  Language  Model(MLM) tasks. Then it is fine-tuned with the parameters and on the same training datasets as the \textit{BERTreference} model.

\textit{BERTptrn-pero-ocr} The base model is pretrained like the \textit{BERTptrn-reference} model. Then it is fine-tuned with the parameters and on the same training datasets as the \textit{BERTpero-ocr} model.

### 2022-01-18 src-latex/parts/60-results.tex
updated section 5

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{src-latex/figs/eval-ner-exp2.pdf}
    \caption{F1 scores (in \%) of NER predictions in presence of OCR noise in the training and testing data, either manually corrected or OCRed with Pero-OCR and Tesseract. The type of examples used to train the NER task is noted in indice after the model name (e.g. Bert$_{reference}$). Results show that best performances on OCRed entries are obtained when the BERT model has been pretrained and fine-tuned for NER on examples affected with similar OCR errors.}
    \label{fig:exp_2_eval_ner}
\end{figure}
Opt. use synthetic text perturbation as well? Maybe not interesting and too artificial if we have access to 2+ OCR systems.
(original OCR from BNF, Tesseract 4, Pero OCR…)

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{src-latex/figs/eval-ner-exp2.pdf}
    \caption{F1 scores (in \%) of NER predictions in presence of OCR noise in the training and testing examples, either manually corrected or raw from Pero-OCR and Tesseract. The type of examples used to train the NER task is noted in indice after the model name (e.g. Bert$_{reference}$). Results show that best performances on OCRed entries are obtained when the BERT model has been pretrained and fine-tuned for NER on examples affected with similar OCR errors.}
    \label{fig:exp_2_eval_ner}
\end{figure}
Opt. use synthetic text perturbation as well? Maybe not interesting and too artificial if we have access to 2+ OCR systems.
(original OCR from BNF, Tesseract 4, Pero OCR…)
